Monte Carlo Expectation Maximization for RNAseq

### 2015-06-17 slides/EM/em.Rnw
increase G and n_iter

<<heterosis_data, cache=TRUE>>=
G = 10
n = 4
truth = data.frame(mu_phi   = 3, tau_phi   = 1, mu_psi = 0, tau_psi = 1,
                   mu_alpha = 0, tau_alpha = 1, mu_delta = 0, tau_delta = .1^2)
par = data.frame(gene=1:G, 
                 phi   = with(truth, rnorm(G, mu_phi  , sqrt(tau_phi  ))),
                 alpha = with(truth, rnorm(G, mu_alpha, sqrt(tau_alpha))),
                 delta = with(truth, rnorm(G, mu_delta, sqrt(tau_delta))),
                 psi   = with(truth, rnorm(G, mu_psi  , sqrt(tau_psi  ))))
X = cbind(1, rep(c(-1,1,0), each=n), rep(c(0,0,1), each=n))
d = ddply(par, .(gene), function(x) {
  pad = with(x, c(phi,alpha,delta))
  data.frame(y = rnbinom(3*n, mu = exp(X%*%pad), size=1/exp(x$psi)),
             variety = rep(1:3, each=n))
})
@

<<heterosis_mcmcem, dependson=c('negative_binomial_data','negative_binomial_stan'), cache=TRUE, echo=FALSE, results='hide'>>=
current = as.list(truth)
n_iter = 10
keep = data.frame(iteration = 1:n_iter, 
                  mu_phi    = rep(NA, n_iter), 
                  mu_alpha  = rep(NA, n_iter), 
                  mu_delta  = rep(NA, n_iter), 
                  mu_psi    = rep(NA,n_iter),
                  tau_phi   = rep(NA, n_iter),
                  tau_alpha = rep(NA, n_iter), 
                  tau_delta = rep(NA, n_iter),
                  tau_psi   = rep(NA,n_iter))

>>>>

<<heterosis_data, cache=TRUE>>=
G = 100
n = 4
truth = data.frame(mu_phi   = 3, tau_phi   = 1, mu_psi = 0, tau_psi = 1,
                   mu_alpha = 0, tau_alpha = 1, mu_delta = 0, tau_delta = .1^2)
par = data.frame(gene=1:G, 
                 phi   = with(truth, rnorm(G, mu_phi  , sqrt(tau_phi  ))),
                 alpha = with(truth, rnorm(G, mu_alpha, sqrt(tau_alpha))),
                 delta = with(truth, rnorm(G, mu_delta, sqrt(tau_delta))),
                 psi   = with(truth, rnorm(G, mu_psi  , sqrt(tau_psi  ))))
X = cbind(1, rep(c(-1,1,0), each=n), rep(c(0,0,1), each=n))
d = ddply(par, .(gene), function(x) {
  pad = with(x, c(phi,alpha,delta))
  data.frame(y = rnbinom(3*n, mu = exp(X%*%pad), size=1/exp(x$psi)),
             variety = rep(1:3, each=n))
})
@

<<heterosis_mcmcem, dependson=c('negative_binomial_data','negative_binomial_stan'), cache=TRUE, echo=FALSE, results='hide'>>=
current = as.list(truth)
n_iter = 100
keep = data.frame(iteration = 1:n_iter, 
                  mu_phi    = rep(NA, n_iter), 
                  mu_alpha  = rep(NA, n_iter), 
                  mu_delta  = rep(NA, n_iter), 
                  mu_psi    = rep(NA,n_iter),
                  tau_phi   = rep(NA, n_iter),
                  tau_alpha = rep(NA, n_iter), 
                  tau_delta = rep(NA, n_iter),
                  tau_psi   = rep(NA,n_iter))
